### 2024-09-18 cognitive-bias.qmd
20240917 - loss aversion & prospect theory

*Loss aversion bias* is the tendency to avoid losses rather than acquiring equivalent gains.
That is, loss aversion (similar to punishment sensitivity, as opposed to reward sensitivity) is the tendency to weigh losses (or punishment) more heavily than gains (or rewards).
Loss aversion is different from [risk aversion](#sec-cognitiveBiasesRiskAversion).
Loss aversion is exemplified when teams play conservatively so as "not to lose" instead of "to win."
In fantasy football, loss aversion may lead managers to start or hold onto underperforming high drafts for too long instead of a starting a more promising player out of fear of losing potential value from their initial investment.

@@

Risk seeking, by contrast, has been observed in entrepreneurs and in generals when all of their options are poor [@Kahneman2011].
In fantasy football, risk seeking may be more likely when a manager has a team full of underperforming players.

>>>>

*Loss aversion bias* is the tendency to avoid losses rather than acquiring equivalent gains.
That is, loss aversion (similar to punishment sensitivity, as opposed to reward sensitivity) is the tendency to weigh losses (or punishment) more heavily than gains (or rewards).
Loss aversion is a key aspect of prospect theory [@Kahneman2011].
The loss aversion ratio indicates the extent to which a person weighs losses greater than gains, and for many people is between 1.5 to 2.5 [@Kahneman2011].
Loss aversion is different from [risk aversion](#sec-cognitiveBiasesRiskAversion).
Loss aversion is exemplified when teams play conservatively so as "not to lose" instead of "to win."
In fantasy football, loss aversion may lead managers to start or hold onto underperforming high drafted players for too long instead of starting a more promising player out of fear of losing potential value from their initial investment.

@@

In mixed gambles, in which it is possible for a person to experience either a gain or a loss, [loss aversion](#sec-cognitiveBiasesLossAversion) tends to lead to risk-averse choices [@Kahneman2011]. 
By contrast, when all of a person's options are poor, people tend to engage in risk seeking, as has been observed in entrepreneurs and in generals [@Kahneman2011].
In fantasy football, risk seeking may be more likely when a manager has a team full of underperforming players and a weak record.
